A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-08-17 for_submission/rvaught_2018.tex
added new folder

\begin{abstract}
%The mass and energy of galactic winds remain poorly constrained via QSO and ``down-the-barrel" absorption line studies. One way to better constrain these %parameters is to measure the spatial extent of the outflow in emission. 
We perform a VLT/FORS2 narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission.   The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing sensitive upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the ouflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
%Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds. Based on these comparisons, if our galaxies do host \ion{Mg}{2} emission, then the predicted \ion{Mg}{2} based on this modeling suggests that these winds are anisotropic and dusty for any scattered \ion{Mg}{2} emission to lie below our 5$\sigma$ detection limits.
\end{abstract}

\keywords{galaxies: evolution, galaxies: absorption lines}

@@

One proposed production mechanism for such P-Cygni profiles is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796\AA, $\lambda_{2796}$, and 2803, \AA $\lambda_{2803}$. Once these transitions are excited, they may only decay back to the ground state. If the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systemic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons travel freely towards the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}). Since the first detection of \ion{Mg}{2} emission in an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$. \ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Weiner2009}, \citethnop{Kornei2013},\citethnop{Erb2012}, \citethnop{Feltre2018}). These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.

@@

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the  GOODS-S field at redshift $z \sim 0.7$. 
We use two filters: a  ``line filter" covering the \ion{Mg}{2} doublet, and a ``continuum filter" that is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs. As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind. These observations allow us to create the first ever high-S/N spatially resolved map of both \ion{Mg}{2} emission and absorption.

In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We describe our method of continuum subtraction in Section \ref{sec.cont_sub}. Analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
Section \ref{sec:results} presents results from this analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec\  is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

@@

The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.

@@

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.75]{../Figures/fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5\arcsec $\times$ 5\arcsec ( or about $ 35 \rm \ kpc \times 35 \rm \ kpc $) .\label{fig:hstims}}
\end{figure*}

\begin{figure*}[!h]
\centering
\gridline{\fig{../Figures/filt_26_spectra.pdf}{0.5\textwidth}{(a)}
          \fig{../Figures/filt_36_spectra.pdf}{0.5\textwidth}{(b)}}
\gridline{\fig{../Figures/filt_03_spectra.pdf}{0.5\textwidth}{(c)}
          \fig{../Figures/filt_64_spectra.pdf}{0.5\textwidth}{(d)}}
           \fig{../Figures/filt_57_spectra.pdf}{0.5\textwidth}{(e)}
\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line). The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted by the filter at each wavelength. Vertical dashed lines indicate the wavelengths of the redshifted \ion{Mg}{2}\ doublet. The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HeII+47 filter for the galaxies shown in panels (a) through (d).}
\label{fig:spec_images}
\end{figure*}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
\caption{\textbf{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
\textbf{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
\label{fig.seeing}}
\end{figure}

\subsection{Supplemental Keck/LRIS spectra}
In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck I Low Resolution Imaging Spectrometer (LRIS) program.  A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).  The spectral coverage of these data extends from ${\sim}3200$ to 8000 \AA.

@@

The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are weighted by the night-flat image and then  average-combined to increase the signal-to-noise of any \ion{Mg}{2} emission. Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

@@

J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\

\hline 
\end{tabular}
\begin{tablenotes}
\small
\item The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' spectral energy distributions with Magphys \citep{duCunha2008} as described in \citet{Rubin_2014}.
\end{tablenotes}
\label{tab:prop}
\end{table*}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{../Figures/HEII_final.png}
\includegraphics[scale=.61]{../Figures/HEII3000_final.png}
\caption{Top: Stacked HeII+47 image of the galaxy sample. Bottom: Stacked HeII3000+48 image of the same pointing. The exposure time of each image is $\approx 10$ hours. Each image shows half of the total FOV, $5' \times 7'$ which contains the full sample of galaxies (indicated by the white arrows). East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

\section{Image Subtraction}\label{sec.cont_sub}
We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the images taken with the filter covering the targeted line emission. For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame. The galaxy excluded from our analysis is J.57. As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transition in this galaxy are equally sampled by both of our filters. When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting the \ion{Mg}{2} continuum. We use this galaxy as check on the quality of our continuum subtraction for reasons.

\subsection{Spectral Correction}
In preparation for continuum subtraction, we first consider whether the continuum level of each galaxy spectrum changes significantly over the passbands of our two filters.
We use the supplementary spectra from \citet{Rubin_2014} to fit the continuum and determine the spectral slope of each galaxy. We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package \citep{Prochaska2016}\footnote{https://github.com/linetools/linetools} to fit the continuum. We then find the total continuum flux in each filter by convolving the fitted continuum with each filter's transmission curve. Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction. Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{../Figures/stamps.pdf}
\caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample. Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$ measured in the HeII/3000+48 filter. Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII+47 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the \ion{Mg}{2} images.}
\label{fig:stamp_images}
\end{figure*}

@@

\begin{figure*}
\centering
\gridline{\fig{../Figures/J_26.pdf}{0.5\textwidth}{(a)}
          \fig{../Figures/J_36.pdf}{0.5\textwidth}{(b)}}
\gridline{\fig{../Figures/J_03.pdf}{0.5\textwidth}{(c)}
          \fig{../Figures/J_64.pdf}{0.5\textwidth}{(d)}}
           \fig{../Figures/J_57.pdf}{0.5\textwidth}{(e)}
\caption{SB profiles for our sample galaxies. (Top panel) Continuum SB profile (black) measured for each galaxy. The green points show the Mg II + continuum SB measured for the galaxy in the pre-continuum subtracted image. The blue points show the Mg II line SB measured for the galaxy in the continuum subtracted line emission image.  The profile exhibits SB decrements from \ion{Mg}{2} absorption. Photometry was performed in circular annuli. (Bottom panel) The vertical hashes in the bottom show the inner and outer radius of each annulus in kpc. Distance from the center of the galaxy (x-axis) is computed using the average value of the inner and outer radii of each annulus.}
\label{fig:sb_profiles}
\end{figure*}

@@

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{../Figures/hist_sblim.pdf}
\caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values for random circular annuli placed on the continuum-subtracted line image. $F_{\text{src}}$ is the total flux within an aperture and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$. The black arrows point to the statistical significance of the flux inside the ``extended annulus'' of each galaxy.}
\label{fig:limits}
\end{figure}

@@

\begin{figure*}[p]
\centering
\includegraphics[scale=1.2]{../Figures/sigmas.pdf}
\caption{Continuum-subtracted $\chi_{\text{smooth}}$ images of the 5 galaxies in our sample. Every galaxy is placed in the same row in each column. The columns show simulated emission, with brightness of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.  Each image has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$). Each image shows the galaxy along with the same isophotal contour used in previous figures (in black).}
\label{fig:sigmas}
\end{figure*}

@@

\begin{figure*}
\centering
\gridline{\fig{../Figures/J26EW.pdf}{0.8\textwidth}{(a: J.26)}}
 \gridline{\fig{../Figures/J36EW.pdf}{0.8\textwidth}{(b: J.36)}}
\gridline{\fig{../Figures/J03EW.pdf}{0.8\textwidth}{(c: J.03)}}
 \gridline{\fig{../Figures/J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
\caption{Left: Image of the equivalent widths EW$_{\text{\ion{Mg}{2}}}$ inside the red 1SB$_1$ contour. The white contour represents the 0.9\arcsec aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectrum of each galaxy. Middle: Distribution of  EW$_{\text{\ion{Mg}{2}}}$ values in pixels with continuum flux S/N greater than 1.5 inside the slit aperture. Right: The EW$_{\text{\ion{Mg}{2}}}$ values vs. projected in distance from center are in black and binned EW$_{\text{\ion{Mg}{2}}}$ measurements are shown in red. The horizontal error bars in the radial axis represent the width of the radial bin used.}
\label{fig:ews}
\end{figure*}

@@

\bibliography{references2017}

>>>>

\begin{abstract}
We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission. The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing sensitive upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the ouflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
\end{abstract}

\keywords{galaxies: evolution -- galaxies: halo}

@@

One proposed production mechanism for such P-Cygni profiles is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796.35\AA\ ($\lambda_{2796}$) and 2803.53\AA\ ($\lambda_{2803}$) \citep{Morton2003}. Once these transitions are excited, they may only decay back to the ground state. If the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systemic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons travel freely towards the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}). Since the first detection of \ion{Mg}{2} emission in an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$. \ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck DEep Imaging Multi-Object Spectrograph (DEIMOS) and VLT Multi Unit Spectroscopic Explorer (MUSE)  (\citethnop{Weiner2009}, \citethnop{Kornei2013},\citethnop{Erb2012}, \citethnop{Feltre2018}). These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.

@@

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey South (GOODS-S; \citethnop{Giavalisco2004})  field at redshift $z \sim 0.7$. 
We use two filters: a  ``line filter" covering the \ion{Mg}{2} doublet, and a ``continuum filter" that is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs. As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind. These observations allow us to create the first ever high-S/N spatially resolved map of both \ion{Mg}{2} emission and absorption.

In Section \ref{sec:obs_red} we describe our sample of GOODS-S galaxies, supplemental Keck I Low Resolution Imaging Spectrometer (Keck/LRIS) spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We describe our method of continuum subtraction in Section \ref{sec.cont_sub}. Analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
Section \ref{sec:results} presents results from this analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec\  is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

@@

The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions (SED) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.

@@

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.75]{fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5\arcsec $\times$ 5\arcsec ( or about $ 35 \rm \ kpc \times 35 \rm \ kpc $) .\label{fig:hstims}}
\end{figure*}

\begin{figure*}[!h]
\centering
\gridline{\fig{filt_26_spectra.pdf}{0.5\textwidth}{}
          \fig{filt_36_spectra.pdf}{0.5\textwidth}{}}
\gridline{\fig{filt_03_spectra.pdf}{0.5\textwidth}{}
          \fig{filt_64_spectra.pdf}{0.5\textwidth}{}}
           \fig{filt_57_spectra.pdf}{0.5\textwidth}{}
\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line). The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted by the filter at each wavelength. Vertical dashed lines indicate the wavelengths of the redshifted \ion{Mg}{2}\ doublet. The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HeII+47 filter for the galaxies shown in panels (a) through (d).}
\label{fig:spec_images}
\end{figure*}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
\caption{\textbf{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
\textbf{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
\label{fig.seeing}}
\end{figure}

\subsection{Supplemental Keck/LRIS spectra}
In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck/LRIS program.  A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).  The spectral coverage of these data extends from ${\sim}3200$ to 8000 \AA.

@@

The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep[e.g.,][]{Battaia_2015}. 
The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are weighted by the night-flat image and then  average-combined to increase the signal-to-noise of any \ion{Mg}{2} emission. Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

@@

J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
\hline 
\end{tabular}
\tablenotemark{}
\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SED with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
\label{tab:prop}
\end{table*}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{HEII_final.png}
\includegraphics[scale=.61]{HEII3000_final.png}
\caption{Top: Stacked HeII+47 image of the galaxy sample. Bottom: Stacked HeII3000+48 image of the same pointing. The exposure time of each image is $\approx 10$ hours. Each image shows half of the total FOV, $5' \times 7'$ which contains the full sample of galaxies (indicated by the white arrows). East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

\section{Image Subtraction}\label{sec.cont_sub}
We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the images taken with the filter covering the targeted line emission. For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame. The galaxy excluded from our analysis is J.57. As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transitions in this galaxy are equally sampled by both of our filters. When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting both \ion{Mg}{2} emission (if present) and the continuum. We thus use this galaxy as check on the quality of our continuum subtraction.

\subsection{Spectral Correction}
In preparation for continuum subtraction, we first consider whether the continuum level of each galaxy spectrum changes significantly over the passbands of our two filters.
We use the supplementary spectra from \citet{Rubin_2014} to fit the continuum and determine the spectral slope of each galaxy. We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package \citep{Prochaska2016}\footnote{https://github.com/linetools/linetools} to fit the continuum. We then find the total continuum flux in each filter by convolving the fitted continuum with each filter's transmission curve. Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction. Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{stamps.pdf}
\caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample. Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$ measured in the HeII/3000+48 filter. Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII+47 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the \ion{Mg}{2} images.}
\label{fig:stamp_images}
\end{figure*}

@@

\begin{figure*}
\centering
\gridline{\fig{J_26.pdf}{0.5\textwidth}{}
          \fig{J_36.pdf}{0.5\textwidth}{}}
\gridline{\fig{J_03.pdf}{0.5\textwidth}{}
          \fig{J_64.pdf}{0.5\textwidth}{}}
           \fig{J_57.pdf}{0.5\textwidth}{}
\caption{SB profiles for our sample galaxies. (Top panel) Continuum SB profile (black) measured for each galaxy. The green points show the Mg II + continuum SB measured for the galaxy in the pre-continuum subtracted image. The blue points show the Mg II line SB measured for the galaxy in the continuum subtracted line emission image.  The profile exhibits SB decrements from \ion{Mg}{2} absorption. Photometry was performed in circular annuli. (Bottom panel) The vertical hashes in the bottom show the inner and outer radius of each annulus in kpc. Distance from the center of the galaxy (x-axis) is computed using the average value of the inner and outer radii of each annulus.}
\label{fig:sb_profiles}
\end{figure*}

@@

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{hist_sblim.pdf}
\caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values for random circular annuli placed on the continuum-subtracted line image. $F_{\text{src}}$ is the total flux within an aperture and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$. The black arrows point to the statistical significance of the flux inside the ``extended annulus'' of each galaxy.}
\label{fig:limits}
\end{figure}

@@

\begin{figure*}[p]
\centering
\includegraphics[scale=1.2]{sigmas.pdf}
\caption{Continuum-subtracted $\chi_{\text{smooth}}$ images of the 5 galaxies in our sample. Every galaxy is placed in the same row in each column. The columns show simulated emission, with brightness of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.  Each image has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$). Each image shows the galaxy along with the same isophotal contour used in previous figures (in black).}
\label{fig:sigmas}
\end{figure*}

@@

\begin{figure*}
\centering
\gridline{\fig{J26EW.pdf}{0.8\textwidth}{(a: J.26)}}
 \gridline{\fig{J36EW.pdf}{0.8\textwidth}{(b: J.36)}}
\gridline{\fig{J03EW.pdf}{0.8\textwidth}{(c: J.03)}}
 \gridline{\fig{J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
\caption{Left: Image of the equivalent widths EW$_{\text{\ion{Mg}{2}}}$ inside the red 1SB$_1$ contour. The white contour represents the 0.9\arcsec aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectrum of each galaxy. Middle: Distribution of  EW$_{\text{\ion{Mg}{2}}}$ values in pixels with continuum flux S/N greater than 1.5 inside the slit aperture. Right: The EW$_{\text{\ion{Mg}{2}}}$ values vs. projected in distance from center are in black and binned EW$_{\text{\ion{Mg}{2}}}$ measurements are shown in red. The horizontal error bars in the radial axis represent the width of the radial bin used.}
\label{fig:ews}
\end{figure*}

@@

\newpage
\bibliography{references2017}
